True versus apparent shapes of bow shocks and bow waves

### 2017-10-14 papers/Paper1/sec-thin-shell.tex
Revamped Fig 16 with the [[an]cara]wilkinoids on Rc-R90 diagram
Split into two panels for clarity.  Annotated with i* where we switch
over from the head to the tail for R90
Add new figures to cantoid section and remove unwanted ones

\newcommand\iso{\ensuremath{^{\mathrm{iso}}}}

\begin{table}
  \caption{Coefficients for hyperbola fit to bowshock tails}
  \label{tab:tail-fit-coeffs}
  \renewcommand\arraystretch{1.2}
  \setlength\tabcolsep{0.5\tabcolsep}
  \begin{tabular}{@{}llll@{}}
    \toprule
    Equation~(\ref{eq:tail-analytic-x0}) & 
    \multicolumn{3}{l}{
    Equation~(\ref{eq:tail-analytic-coeffs-c}) \dotfill
    } \\ \midrule
    \( C\iso_0 = +1.3195     \)    
    & \( c_{0,0} = +2.0758   \)  
    & \( c_{1,0} = -0.2309   \)  
    & \( c_{2,0} = -0.2532   \)\\
      \( C\iso_1 = +0.4229     \)    
    & \( c_{0,1} = +0.9571   \)  
    & \( c_{1,1} = -0.1530   \)  
    & \( c_{2,1} = -0.2487   \)\\
      \( C\iso_2 = +0.1092     \)    
    & \( c_{0,2} = +0.2528   \)  
    & \( c_{1,2} = -0.0360   \)  
    & \( c_{2,2} = -0.0794   \)\\
      \( C\iso_3 = +0.0051     \)    
    & \( c_{0,3} = +0.0171   \)  
    & \( c_{1,3} = -0.0010   \)  
    & \( c_{2,3} = -0.0095   \)\\ \midrule
    Equation~(\ref{eq:tail-analytic-x0-minus-a}) &
    \multicolumn{3}{l}{
    Equation~(\ref{eq:tail-analytic-coeffs-d}) \dotfill
    } \\ \midrule
    \( D\iso_0 = +0.7962   \)    
    & \( d_{0,0} = +0.8516 \)  
    & \( d_{1,0} = -0.0907 \)  
    & \( d_{2,0} = -0.2002 \)\\
      \( D\iso_1 = -0.2363   \)    
    & \( d_{0,1} = -0.7620 \)  
    & \( d_{1,1} = +0.1411 \)  
    & \( d_{2,1} = -0.0295 \)\\
      \( D\iso_2 = -0.0126   \)    
    & \( d_{0,2} = -0.0683 \)  
    & \( d_{1,2} = +0.0390 \)  
    & \( d_{2,2} = -0.0236 \)\\
    \bottomrule
  \end{tabular}
\end{table}

\begin{figure*}
  \centering
  \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-analytic}
  \caption{Double quadric fits to thin shell
    solutions.}
  \label{fig:head-tail}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-residuals}
  \caption[]{Residuals of double quadric fits to thin shell solutions.
    Residuals are expressed as the fractional error in the
    complementary angle \(\theta_1\) for the same parameters as are shown
    in Fig.~\ref{fig:head-tail}.}
  \label{fig:head-tail-residuals}
\end{figure*}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/two-quadric-R90-vs-Rc}
  \caption{Diagnostic diagram for thin shell models}
  \label{fig:thin-shell-R90-Rc}
\end{figure}

>>>>

% \newcommand\iso{\ensuremath{^{\mathrm{iso}}}}

% \begin{table}
%   \caption{Coefficients for hyperbola fit to bowshock tails}
%   \label{tab:tail-fit-coeffs}
%   \renewcommand\arraystretch{1.2}
%   \setlength\tabcolsep{0.5\tabcolsep}
%   \begin{tabular}{@{}llll@{}}
%     \toprule
%     Equation~(\ref{eq:tail-analytic-x0}) & 
%     \multicolumn{3}{l}{
%     Equation~(\ref{eq:tail-analytic-coeffs-c}) \dotfill
%     } \\ \midrule
%     \( C\iso_0 = +1.3195     \)    
%     & \( c_{0,0} = +2.0758   \)  
%     & \( c_{1,0} = -0.2309   \)  
%     & \( c_{2,0} = -0.2532   \)\\
%       \( C\iso_1 = +0.4229     \)    
%     & \( c_{0,1} = +0.9571   \)  
%     & \( c_{1,1} = -0.1530   \)  
%     & \( c_{2,1} = -0.2487   \)\\
%       \( C\iso_2 = +0.1092     \)    
%     & \( c_{0,2} = +0.2528   \)  
%     & \( c_{1,2} = -0.0360   \)  
%     & \( c_{2,2} = -0.0794   \)\\
%       \( C\iso_3 = +0.0051     \)    
%     & \( c_{0,3} = +0.0171   \)  
%     & \( c_{1,3} = -0.0010   \)  
%     & \( c_{2,3} = -0.0095   \)\\ \midrule
%     Equation~(\ref{eq:tail-analytic-x0-minus-a}) &
%     \multicolumn{3}{l}{
%     Equation~(\ref{eq:tail-analytic-coeffs-d}) \dotfill
%     } \\ \midrule
%     \( D\iso_0 = +0.7962   \)    
%     & \( d_{0,0} = +0.8516 \)  
%     & \( d_{1,0} = -0.0907 \)  
%     & \( d_{2,0} = -0.2002 \)\\
%       \( D\iso_1 = -0.2363   \)    
%     & \( d_{0,1} = -0.7620 \)  
%     & \( d_{1,1} = +0.1411 \)  
%     & \( d_{2,1} = -0.0295 \)\\
%       \( D\iso_2 = -0.0126   \)    
%     & \( d_{0,2} = -0.0683 \)  
%     & \( d_{1,2} = +0.0390 \)  
%     & \( d_{2,2} = -0.0236 \)\\
%     \bottomrule
%   \end{tabular}
% \end{table}

% \begin{figure*}
%   \centering
%   \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-analytic}
%   \caption{Double quadric fits to thin shell
%     solutions.}
%   \label{fig:head-tail}
% \end{figure*}

% \begin{figure}
%   \centering
%   \includegraphics[width=\linewidth]{figs/two-quadric-th90-vs-i}
%   \caption{Variation with inclination of the body-frame polar angle
%     \(\theta_{90}\) that corresponds to the projected perpendicular radius
%     \(R’_{90}\).  Line colors and thicknesses represent different
%     quadrics of revolution, as in
%     Fig.~\ref{fig:projected-R90-Rc-snapshots}.  This quantity is
%     important because the quadric fits to the bow shock shape must be
%     accurate for \(\theta < \theta_{90}\) in order to give a reliable estimate
%     for \(R’_{90}\).}
%   \label{fig:projected-th90}
% \end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=0.8\textwidth]{figs/conic-head-tail-residuals}
  \caption[]{Residuals of double quadric fits to thin shell solutions.
    Residuals are expressed as the fractional error in the
    complementary angle \(\theta_1\) (see Fig.~\ref{fig:crw-schema}) for
    the same parameters as are shown in Fig.~\ref{fig:head-tail}.}
  \label{fig:head-tail-residuals}
\end{figure*}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/test_xyprime}
  \caption{Apparent bow shapes as a function of inclination angle for
    isotropic thin shell models. (a)~Confocal paraboloid for
    comparison (shape independent of inclination).
    (b)~Wilkinoid. (c)~Cantoid, \(\beta = 0.001\). (d)~Cantoid,
    \(\beta = 0.01\). }
  \label{fig:xyprime}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/test_xyprime_ancantoid}
  \caption{Further apparent bow shapes as a function of inclination
    angle for anisotropic thin shell models (ancantoids).
    (a)~\(\beta = 0.001\), \(\xi =.8\); (b) (a)~\(\beta = 0.1\),
    \(\xi =.8\); (c)~\(\beta = 0.001\) \(\xi =0.4\); (d)
    \(\beta = 0.1\) \(\xi =0.4\).}
  \label{fig:xyprime-anacantoid}
\end{figure}

\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.48\linewidth}
  \begin{tabular}{@{}ll@{}}
    (a) & (b) \\
    \includegraphics{figs/ancantoid-R90-vs-Rc-a}
        & \includegraphics{figs/ancantoid-R90-vs-Rc-b} \\
  \end{tabular}
  \caption{Diagnostic diagram for thin shell models}
  \label{fig:thin-shell-R90-Rc}
\end{figure*}
